\section{INTRODUCTION}

\subsection{Purpose of this document}
The purpose of this document is to describe the acceptance test procedures for the BusPlanner project. These tests will be used to verify that the product meets the requirements presented in the Requirements Document.

\subsection{Document organization}
The document is organized as follows:
\begin{itemize}
	\item Section 1, \textit{Introduction}, gives an overview of this document describing its contents, scope etc.
	\item Section 2, \textit{Test Plan}, describes the testing process, items and environment.
	\item Section 3, \textit{Acceptance Tests}, describes the test cases.
\end{itemize}

\subsection{Intended audience}
The intended audience of this document is composed of:
\begin{itemize}
	\item Development team.
	\item Team supervisors:
	\begin{itemize}
		\item Abhilash Thekkilakattil (MDH).
		\item Elisabetta Di Nitto (POLIMI).
	\end{itemize}
	\item Project customer: Aneta Vulgarakis Feljan (Ericsson).
	\item Stakeholders.
	\item Any developer who is interested into improving our project.
\end{itemize}

\subsection{Scope}
This document aims to describe the testing process and its purpose, that is to ensure the application meets all of its requirements	. For this reason it includes the features and testing procedures, criteria for passing tests and the expected results. 

\subsection{Definitions and Acronyms}

\subsubsection{Definitions}
\begin{center}
	\begin{tabular} { | m{3.5cm} | m{9.5cm} | }
		\hline
		\textbf{Keyword} & \textbf{Definitions}\\
		\hline
		User & A person who requests buses.\\
		\hline
		Fleet Manager & They own the buses and they are the resource managers of the company.\\
		\hline
		Bus Driver & The driver of the company's buses.\\
		\hline
		User Request & Request generated by the users that choose the stops where they want to get on and off the bus.\\
		\hline
		Algorithm & A method used to enhance the scheduling process (static and dynamic).\\
		\hline
		Sprint & A repeatable work cycle which is also known as iteration.\\
		\hline
		Project Customer & The customer who requested the software product.\\
		\hline
		Acceptance Test & The process of verifying that a solution works for the user.\\
		\hline
	\end{tabular}
\end{center}
\subsubsection{Acronyms and abbreviations}
\begin{center}
	\begin{tabular} { | m{5cm} | m{8cm} | }
		\hline
		\textbf{Acronym/abbreviation} & \textbf{Definitions}\\
		\hline
		UI & User Interface\\
		\hline
		GUI & Graphical User Interface\\
		\hline
		MDH & Mälardalens Högskola, Västerås, Sweden\\
		\hline
		POLIMI & Politecnico di Milano, Milan, Italy\\
		\hline
		QA & Quality Assurance\\
		\hline
		DSD & Distributed Software Development\\
		\hline
	\end{tabular}
\end{center}