\section{INTRODUCTION}
\subsection{Purpose of this document}
The purpose of this document is to give an overview of the project design i-e functionalities, Class diagram, Software architecture, Graphical User Interface and Database Model.
\subsection{Document organization} 
The document is organized as follows:
\begin{itemize}
	\item Section 1, Description and definitions describes the content of the design document.
	\item Section 2, Background and objectives describes the purpose of the project and the algorithm used for reducing the number of buses per route and the time needed to do a scheduling.
	\item Section 3, High level system architecture describes the system's main components such as MySQL, the BusPlanner application and the user simulation.
	\item Section 4, Software architecture describes the system's architecture layers (presentation layer, business logic layer and data access layer) and the technologies used to implement them (HTML, CSS, Bootstrap, PHP and MySQL). 
	\item Section 5, Graphical User Interface presents the web pages models the users will interact with.
	\item Section 6, Database model describes the format of the tables needed to store and retrieve data.
\end{itemize}
\subsection{Intended Audience} 
The intended audience of this document is composed of:
\begin{itemize}
\item Development team, as a guidance line during development and also for the team to ensure that they have the same level of understanding on the project design, architecture and technologies used.
\item Stakeholders, whose needs will be taken under consideration in the design and architecture of the project.
\end{itemize}
\subsection{Scope} 
This document will provide an overview about the project design, architecture and technologies used during the development of the project. It also presents the database model.
The document will be a guideline for the development team during the development process, saving them a lot of time.  
\subsection{Definitions and acronyms}
\subsubsection{Definitions} 
\begin{center}
	\begin{tabular} { | m{3cm} | m{10cm} | }
		\hline
		\textbf{Keyword} & \textbf{Definitions}\\
		\hline
		User & A person who requests for bus by being from bus stop.\\
		\hline
		Fleet Manager & Who owns the buses. He/she wants to know the utilization of buses and scheduling of buses.\\
		\hline
		User Request & Information generated with timestamps for the scheduling purpose.\\
		\hline
		Algorithm & A method used to enhance the scheduling process which is static as well as dynamic.\\
		\hline
		Sprint & A repeatable work cycle which is also known as iteration.\\
		\hline
	\end{tabular}
\end{center}
\subsubsection{Acronyms and abbreviations}
\begin{center}
	\begin{tabular} { | m{5cm} | m{8cm} | }
		\hline
		\textbf{Acronym/abbreviation} & \textbf{Definitions}\\
		\hline
		UI & User Interface\\
		\hline
		GUI & Graphical User Interface\\
		\hline
		MDH & Mälardalens Högskola, Västerås, Sweden\\
		\hline
		POLIMI & Politecnico di Milano, Milan, Italy\\
		\hline
		QA & Quality Assurance\\
		\hline
		DSD & Distributed Software Development\\
		\hline
	\end{tabular}
\end{center}