\section{INTRODUCTION}

\subsection{Purpose of this document}
The purpose of this document is to show the results of the automatic test procedures applied to the test cases described in the \textit{Acceptance Test Plan} document. 

\subsection{Document organization}
The document is organized as follows:
\begin{itemize}
	\item Section 1, \textit{Introduction}, gives an overview of this document describing its contents, scope etc.
	\item Section 2, \textit{Test Cases and Results}, describes the test cases and the related results obtained from the manual and automatic testing.
\end{itemize}

\subsection{Intended audience}
The intended audience of this document is composed of:
\begin{itemize}
	\item Development team.
	\item Team supervisors:
	\begin{itemize}
		\item Abhilash Thekkilakattil (MDH).
		\item Elisabetta Di Nitto (POLIMI).
	\end{itemize}
	\item Project customer: Aneta Vulgarakis Feljan (Ericsson).
	\item Stakeholders.
	\item Any developer who is interested into improving our project.
\end{itemize}

\subsection{Scope}
This document aims to show the different types of tests the team has performed against the application, following the plan presented in the \textit{Acceptance Test Plan} document.

\subsection{Definitions and Acronyms}

\subsubsection{Definitions}
\begin{center}
	\begin{tabular} { | m{3.5cm} | m{9.5cm} | }
		\hline
		\textbf{Keyword} & \textbf{Definitions}\\
		\hline
		User & A person who requests buses.\\
		\hline
		Fleet Manager & They own the buses and they are the resource managers of the company.\\
		\hline
		Bus Driver & The driver of the company's buses.\\
		\hline
		User Request & Request generated by the users that choose the stops where they want to get on and off the bus.\\
		\hline
		Algorithm & A method used to enhance the scheduling process (static and dynamic).\\
		\hline
		Sprint & A repeatable work cycle which is also known as iteration.\\
		\hline
		Project Customer & The customer who requested the software product.\\
		\hline
		Acceptance Test & The process of verifying that a solution works for the user.\\
		\hline
	\end{tabular}
\end{center}
\subsubsection{Acronyms and Abbreviations}
\begin{center}
	\begin{tabular} { | m{5cm} | m{8cm} | }
		\hline
		\textbf{Acronym/abbreviation} & \textbf{Definitions}\\
		\hline
		UI & User Interface\\
		\hline
		GUI & Graphical User Interface\\
		\hline
		MDH & M\"{a}lardalens H\"{o}gskola, V\"{a}ster\r{a}s, Sweden\\
		\hline
		POLIMI & Politecnico di Milano, Milan, Italy\\
		\hline
		QA & Quality Assurance\\
		\hline
		DSD & Distributed Software Development\\
		\hline
	\end{tabular}
\end{center}

\subsection{Referenced documents}
\begin{itemize}
	\item Requirements Definition document.
	\item Acceptance Test Plan document.
\end{itemize}