\section{INTRODUCTION}
\subsection{Purpose of this document}
The purpose of this document is to provide the project plan, project vision and team organization of the “BusPlanner” project. 
\subsection{Document organization}
The document is organized as follows:
\begin{itemize}
	\item Section 1, Introduction describes the content of this project plan document.
	\item Section 2, Background and Objectives describes the identified problem, goals of the project and high level requirements.
	\item Section 3, Project Organization describes how the project members are organized and the tools used for development and collaboration.
	\item Section 4, Development process describes how the scrum process is planned for our development activities.
	\item Section 5, Deliverables describes the list of deliverables to be delivered as part of this project.
	\item Section 6, Project plan describes the time plan scheduled for this project.
	\item Section 7, Project risk describes the potential risks identified in advance that might occur in the project and the mitigations planned to avoid/solve such risks.	
\end{itemize}
\subsection{Intended audience}
The intended audience of this document are:
\begin{itemize}
	\item Development team, as a guidance during the development activities and for the team to ensure that they have the same level of understanding on the project vision.
	\item Stakeholders, as an information regarding the plan and scope of the project.	
\end{itemize}
\subsection{Scope}
This document will provide an overview about our project, required actions to be done and also the development process which we follow.
This document will serve as a foundation for creating the document containing requirements analysis and design.
\subsection{Definitions and Acronyms}
\subsubsection{Definitions}
\begin{center}
	\begin{tabular} { | m{3cm} | m{10cm} | }
		\hline
		\textbf{Keyword} & \textbf{Definitions}\\
		\hline
		User & A person who requests for bus by being from bus stop.\\
		\hline
		Fleet Manager & Who owns the buses. He/she wants to know the utilization of buses and scheduling of buses.\\
		\hline
		User Request & Information generated with timestamps for the scheduling purpose.\\
		\hline
		Algorithm & A method used to enhance the scheduling process which is static as well as dynamic.\\
		\hline
		Sprint & A repeatable work cycle which is also known as iteration.\\
		\hline
	\end{tabular}
\end{center}
\subsubsection{Acronyms and abbreviations}
\begin{center}
	\begin{tabular} { | m{5cm} | m{8cm} | }
		\hline
		\textbf{Acronym/abbreviation} & \textbf{Definitions}\\
		\hline
		UI & User Interface\\
		\hline
		GUI & Graphical User Interface\\
		\hline
		MDH & Mälardalens Högskola, Västerås, Sweden\\
		\hline
		POLIMI & Politecnico di Milano, Milan, Italy\\
		\hline
		QA & Quality Assurance\\
		\hline
		DSD & Distributed Software Development\\
		\hline
	\end{tabular}
\end{center}