\section{ORGANIZATION}
\subsection{Project group}
Our team working on “BusPlanner“ is composed of 7 members located in 2 universities as follows:
\begin{enumerate}
	\item Team members located in MDH Sweden:
	\begin{itemize}
		\item Albi Dode
		\item Huy Hoang Nguyen
		\item Muhammad Ejaz Khan
		\item Sharvathul Hasan Ameerjan	
	\end{itemize}
	\item Team members located in POLIMI Italy:
	\begin{itemize}
		\item Andrea Colombo
		\item Isabella Agosti
		\item Stefano Antonino Badalucco	
	\end{itemize}
\end{enumerate}
More information on the members can be found at: \\
\url{http://www.fer.unizg.hr/rasip/dsd/projects/busplanner}
\subsection{Roles}
In our development process we will use SCRUM. The scrum roles are as follows:
\begin{itemize}
	\item Product owner - Isabella Agosti
	\item Scrum master:
	\begin{itemize}
		\item Albi Dode (from the beginning to 01-12-2016).
		\item Stefano Antonino Badalucco (from 01-12-2016).
	\end{itemize}
\end{itemize}
Every team member will contribute equally in the coding and documentation process.
\subsection{Customer}
The customer is Aneta Vulgarakis Feljan from Ericsson.
\subsection{Supervisor}
The team will have two supervisors for the project: 
\begin{enumerate}
	\item Abhilash Thekkilakattil - From MDH
	\item Elisabetta Di Nitto - From Polimi
\end{enumerate}
\subsection{Communication}
The communication between the team members is done every day, mainly using WhatsApp. This was thought to be the fastest way since the team members are in different countries.

For documentation purposes and when new updates are made at the code or documentation, Google Drive comes in help. The audio/video calls with the customer and supervisors are done using Skype.

Each member keeps trace of the working hours and discussions done in the group and daily SCRUM meetings.
\subsection{Tools}
\textbf{Skype} - Mostly used for communicating with the customer or supervisors and also between the team members.\\
\textbf{GitHub} - Used for code sharing, version control.\\
\textbf{WhatsApp} - Used for instant messaging.\\
\textbf{Google Drive} - Used for documents.