\section{DEVELOPMENT PROCESS}
\subsection{SCRUM Overview}
The team has adopted the SCRUM software development methodology for the following reasons:
\begin{itemize}
	\item It organizes the development process in a way that the problem of requirements volatility and unpredicted changes to the software project is addressed in a robust and relatively simple manner.
	\item It promotes team working and communication.
	\item It imposes a systematic-way-based approach through sprints, meetings and sprint backlogs.
\end{itemize}

\subsection{Sprints}
\subsubsection{Sprint 1: 14/11 $\Rightarrow$ 28/11}
\begin{itemize}
	\item Fleet Manager can log into the system. 
	\item Fleet Manager is able to manage buses.
	\item Bus Driver can log into the system.	
\end{itemize}

\subsubsection{Sprint 2: 28/11 $\Rightarrow$ 12/12}
\begin{itemize}
	\item Fleet Manager can manage drivers.
	\item Fleet Manager can get the buses position.
	\item Fleet Manager can manage routes.
	\item Bus Driver can view his personal schedule.
\end{itemize}

\subsubsection{Sprint 3: 12/12 $\Rightarrow$ 10/01}
\begin{itemize}
	\item Fleet Manager can view all the pendant user requests on the map.
	\item Fleet Manager can view all the previous user requests.
	\item Fleet Manager can get the utilization of each route.
	\item The algorithm assigns buses to routes based on the requests.	
\end{itemize}

\subsection{Meetings}
We did:
\begin{itemize}
	\item Daily scrum meetings to assign tasks for the following days. 
	\item Weekly meetings with supervisors (every Friday at 13:30).
	\item Weekly internal meetings right after the meetings with supervisors.
\end{itemize} 
During the meetings we experienced:
\begin{itemize}
	\item Varying number of participants.
	\item Difficulties in dividing the work for the algorithm and testing part.
\end{itemize}

4.2.1 SCRUM implementation and project plan......................................................
4.2.2 Project Plan
4.2.3 Scrum roles
4.2.4 Development Team organization
4.2.5 Contact with the customer
4.2.6 Daily meetings, sprint review meetings
4.2.7 Activities performed before the starting of the first sprint
4.2.8 Sprints 
Sprint 1
Sprint 2
Sprint 3
4.3 Process statistics
4.3.1 Working hours
4.3.2 Contributions
