\section{INTRODUCTION} 
\subsection{Purpose of this document}
The purpose of this document is to summarize the experiences related to the BusPlanner project, both in terms of produced results and project work.

\subsection{Document organization}
The document is organized as follows:
\begin{itemize}
	\item Section 1, \textit{Introduction}, gives an overview of this document describing its contents, scope etc.
	\item Section 2, \textit{}
\end{itemize}

\subsection{Intended Audience}
The intended audience of this document is composed of:
\begin{itemize}
	\item Development team.
	\item Team supervisors:
	\begin{itemize}
		\item Abhilash Thekkilakattil (MDH).
		\item Elisabetta Di Nitto (POLIMI).
	\end{itemize}
	\item Project customer: Aneta Vulgarakis Feljan (Ericsson).
	\item Stakeholders.
	\item Any developer who is interested into improving our project.
\end{itemize}

\subsection{Scope}
This document aims to summarize all the activities regarding the DSD project and at the same time make some reflections about the development process. It also provides some metrics that will help the developers analyze the performances and the level of organization. 

\subsection{Definitions and acronyms} 
\subsubsection{Definitions}
\begin{center}
	\begin{tabular} { | m{3.5cm} | m{9.5cm} | }
		\hline
		\textbf{Keyword} & \textbf{Definitions}\\
		\hline
		User & A person who requests buses.\\
		\hline
		Fleet Manager & They own the buses and they are the resource managers of the company.\\
		\hline
		Bus Driver & The driver of the company's buses.\\
		\hline
		User Request & Request generated by the users that choose the stops where they want to get on and off the bus.\\
		\hline
		Algorithm & A method used to enhance the scheduling process (static and dynamic).\\
		\hline
		Sprint & A repeatable work cycle which is also known as iteration.\\
		\hline
		Project Customer & The customer who requested the software product.\\
		\hline
		Acceptance Test & The process of verifying that a solution works for the user.\\
		\hline
	\end{tabular}
\end{center}
\subsubsection{Acronyms and Abbreviations}
\begin{center}
	\begin{tabular} { | m{5cm} | m{8cm} | }
		\hline
		\textbf{Acronym/abbreviation} & \textbf{Definitions}\\
		\hline
		UI & User Interface\\
		\hline
		GUI & Graphical User Interface\\
		\hline
		MDH & M\"{a}lardalens H\"{o}gskola, V\"{a}ster\r{a}s, Sweden\\
		\hline
		POLIMI & Politecnico di Milano, Milan, Italy\\
		\hline
		QA & Quality Assurance\\
		\hline
		DSD & Distributed Software Development\\
		\hline
	\end{tabular}
\end{center}

\subsection{References}
\begin{itemize}
	\item Project DSD page:\\ \url{http://www.fer.unizg.hr/rasip/dsd/projects/busplanner}.
	\item Project application page:\\ \url{https://busplanner-f496d.firebaseapp.com}.
	\item Project repository:\\ \url{https://github.com/AndreaColombo/BusPlanner---DSD-project-2016-2017}.
\end{itemize}