\section{ORGANIZATION}
\subsection{Project team}
Our team working on “BusPlanner“ is composed of 7 members located in 2 universities as follows:
\begin{enumerate}
	\item Team members located in MDH Sweden:
	\begin{itemize}
		\item Albi Dode
		\item Huy Hoang Nguyen
		\item Muhammad Ejaz Khan
		\item Sharvathul Hasan Ameerjan	
	\end{itemize}
	\item Team members located in POLIMI Italy:
	\begin{itemize}
		\item Andrea Colombo
		\item Isabella Agosti
		\item Stefano Antonino Badalucco	
	\end{itemize}
\end{enumerate}
More information on the members can be found at: \\
\url{http://www.fer.unizg.hr/rasip/dsd/projects/busplanner}

\subsection{Team roles}
\begin{table}[h]
	\centering
	\begin{tabular}{| m{5.2cm} | m{3.4cm} | m{3.4cm} |}
		\hline
		\textbf{Team member} & \textbf{Role until 01/12/2016} & \textbf{Role from 01/12/2016}\\
		\hline
		Isabella Agosti & Product Owner & Product Owner \\
		\hline
		Stefano Antonino Badalucco & Developer & Scrum Master \\
		\hline
		Andrea Colombo & Developer & Developer \\
		\hline
		Albi Dode & Scrum Master & Developer \\
		\hline
		Huy Hoang Nguyen & Developer & Developer \\
		\hline
		Muhammad Ejaz Khan & Developer & Developer \\
		\hline
		Sharvathul Hasan Ameerjan & Developer & Developer \\
		\hline
	\end{tabular}
\end{table}
\newpage
\subsection{Work division}
\subsubsection*{Front-End team}
\begin{itemize}
	\item Isabella Agosti.
	\item Stefano Antonino Badalucco.
\end{itemize}

\subsubsection*{Back-End team}
\begin{itemize}
	\item Andrea Colombo as static algorithm developer.
	\item Albi Dode as dynamic algorithm developer.
	\item Huy Hoang Nguyen as static algorithm developer and testing.
	\item Muhammad Ejaz Khan for integration.
	\item Sharvathul Hasan Ameerjan as dynamic algorithm developer.
\end{itemize}

\subsection{Customer}
Our customer is Aneta Vulgarakis Feljan from Ericsson. 

\subsection{Supervisors}
The team had two supervisors for the project:
\begin{itemize}
	\item Abhilash Thekkilakattil - From MDH.
	\item Elisabetta Di Nitto - From Polimi.
\end{itemize}
\newpage
\subsection{Used tools}
\begin{itemize}
	\item \textbf{Skype} \\
	For meetings with supervisors and internal meetings.\\
	\url{https://www.skype.com}
	\item \textbf{GitHub} and \textbf{GitHub Desktop} \\
	To collaborate with the team and keep track of the changes in the documents. \\
	\url{https://github.com} and \url{https://desktop.github.com}
	\item \textbf{Balsamiq} \\
	To design the mockups. \\
	\url{https://balsamiq.com}
	\item \textbf{TeXstudio} \\
	LaTeX editor we used to write this document. \\
	\url{http://www.texstudio.org}
	\item \textbf{BasicTeX} \\
	Distribution of the LaTeX system. \\
	\url{http://www.tug.org/mactex/morepackages.html}
	\item \textbf{Google Drive} \\
	For sharing documents.
	\url{https://drive.google.com}
	\item \textbf{WhatsApp} \\
	For instant messages.
	\url{https://www.whatsapp.com}
\end{itemize}